The state of knowledge for marine invertebrate biodiversity in the continental US

### 2018-01-16 manuscript.Rmd
fix typo in calculation

```{r idigbio-mms}
prop_mms_75_85 <- (idigbio_mms_summary_by_year %>%
                   dplyr::filter(year >= 1975 & year <= 1985) %>%
                   dplyr::pull(n) %>%
                   sum()) / dplyr::pull(idigbio_mms_summary_by_year, n)
```

Biodiversity surveys conducted under the auspices of the Bureau of Land Management (BLM) and the Minerals Management Service (MMS) have contributed significantly to our knowledge of the geographic distribution of marine invertebrates in US waters. In our dataset, we identified at least `r format(sum(idigbio_mms_summary_by_year$n), big.mark=",")` records (or `r sum(idigbio_mms_summary_by_year$n)/nrow(idigbio_us_inverts_records_all)*100`% of all US marine invertebrates in iDigBio) from these surveys, `r format_output(prop_mms_75_85 * 100)`% of which were collected between 1975 and 1985. Of the `r idigbio_mms_records %>% filter(rank %in% c("Species", "Subspecies")) %>% summarize(n = n_distinct(worms_valid_name))` species collected as part of these surveys, `r nrow(idigbio_mms_species_only)` have not been collected outside of these surveys.

>>>>

```{r idigbio-mms}
prop_mms_75_85 <- (idigbio_mms_summary_by_year %>%
                   dplyr::filter(year >= 1975 & year <= 1985) %>%
                   dplyr::pull(n) %>%
                   sum()) / sum(dplyr::pull(idigbio_mms_summary_by_year, n))
```

Biodiversity surveys conducted under the auspices of the Bureau of Land Management (BLM) and the Minerals Management Service (MMS) have contributed significantly to our knowledge of the geographic distribution of marine invertebrates in US waters. In our dataset, we identified at least `r format(sum(idigbio_mms_summary_by_year$n), big.mark=",")` records (or `r format_output(sum(idigbio_mms_summary_by_year$n)/nrow(idigbio_us_inverts_records_all)*100)`% of all US marine invertebrates in iDigBio) from these surveys, `r format_output(prop_mms_75_85 * 100)`% of which were collected between 1975 and 1985. Of the `r idigbio_mms_records %>% filter(rank %in% c("Species", "Subspecies")) %>% summarize(n = n_distinct(worms_valid_name)) %>% format(big.mark=",")` species collected as part of these surveys, `r nrow(idigbio_mms_species_only)` have not been collected outside of these surveys.
